\input{myarticlepreamble.tex}
\input{cccs.tex}
\renewcommand\TITLE{CCCS: Fall 2016 Agenda}

\begin{document}
\topmatter


\section{Introduction}
\label{sec:orgheadline1}

This document enumerates key agenda items for Fall 2016 semester for the
Columbia College Computer Science Club. In particular, a rough outline of
planned events is included. More information on the events will be provided as
we approach them but the club hopes that we will generate interest based on the
preliminary information here. Any volunteers are greatly encouraged to
participate in any activity of interest to them.

Please send an email to the CS club officers at cccsofficers@googlegroups.com
if you are interested in any information discussed in this document or have any
other comments pertinent to the club.


\section{Columbia College Computer Science Club}
\label{sec:orgheadline8}

\subsection{Google Group}
\label{sec:orgheadline2}

The CS department has a Google Group that is used as our mailing list. The
group is cc\_cs and the mailing address for the group is cc\_cs@googlegroups.com.
In particular, it is used for department-wide announcments that include club
events and employment opportunities. If you know someone who should be in the
group but isn't (happens a lot with new CS students), please send them our way.

\subsection{Calendar}
\label{sec:orgheadline3}

There's a calendar of events that you can access through the frontpage at
\url{http://bit.ly/yliow0}.

\newpage

\subsection{Club Officers Contact Information}
\label{sec:orgheadline4}

\begin{description}
\item[{Group Email:}] cc.cs.officers@googlegroups.com
\item[{Advisor:}] Dr. Yihsiang Liow (yliow@ccis.edu)
\item[{Officers:}] \hspace*{1em}
\begin{description}
\item[{President:}] Ryan Frappier (rbfrappier1@cougars.ccis.edu)
\item[{Vice-president:}] Faizal Glenn (feglenn1@couars.ccis.edu)
\item[{Treasurer:}] Andrew Woods (amwoods3@cougars.ccis.edu)
\item[{Secretary:}] Rotshak Dakup (rjdakup1@cougars.ccis.edu)
\item Chris Heskett (cjheskett1@cougars.ccis.edu)
\item Garrett Waage (gjwaage1@cougars.ccis.edu)
\item Michael \textquoteleft{}Mikey\textquoteright{} Thomas (mgthomas2@cougars.ccis.edu)
\item Nathan Haggerman (nmhaggerman1@cougars.ccis.edu)
\item Ujjwal Pandey (ujpandey1@cougars.ccis.edu)
\end{description}
\item[{Locations:}] \hspace*{1em}
\begin{description}
\item[{STC 321:}] Computer Science \textquoteleft{}Linux\textquoteright{} Lab
\item[{STC 223:}] Dr. Liow's Office
\item[{BUH 104 / BUH 107:}] Buchanan lab classrooms
\end{description}
\end{description}

\newpage

\subsection{Computer Science Hangouts}
\label{sec:orgheadline5}

We meet every day from 3 to 5 pm in one of the Buchanan labs.

Seniors and Dr. Liow will be in attendance who will help with anything CS
related. Everyone's encouraged to help each other where possible as well.

It's fine to come just to hang out if no help is needed for classwork. It's
also fine to come discuss CS related topics outside of classwork.

We are in Buchanan 107 every weekday except for Mondays. If you don't find us
in BUH107, look around one of the Buchanan rooms and you should see us.

\begin{description}
\item[{WHAT:}] Computer Science Hangouts
\item[{WHY:}] Hangout with others in the department and get help if you need any
\item[{WHEN:}] 3pm to 5 pm, every weekday
\item[{WHERE:}] BUH 107 Tuesdays to Fridays, check around BUH if we aren't there
\end{description}

\subsection{Club Meetings}
\label{sec:orgheadline6}

The club will have meetings on demand. We have events planned throughout the
semester that we will send periodic information about as we approach them
through the Google Group and other channels. We also treat Computer Science
Hangout sessions every Friday from 3 to 5 pm in BUH107 as informal club
meetings. Club members should make every attempt to join the Friday hangout
sessions if possible.

We occassionally meet at other times for various purposes included but not
limited to:
\begin{itemize}
\item workshops on various tools that a programmer should be aware of
\item talks on career planning, searching for internships and jobs, interview
preparation and so on
\item forums on various special interest topics such as game development,
artificial intelligence and more
\item Hackathons to develop prototypes for interesting ideas in limited time
\item Programming contests to celebrate competitive programming
\item presentations from students who want to show off their work
\end{itemize}

We need help to make these events happen! Come up to us if you are interested
or if you have ideas for something else.

\subsection{Other events}
\label{sec:orgheadline7}

We also have social events such as:
\begin{itemize}
\item Movie nights
\item Music Jam sessions
\item Game days
\item Fun(d) raising events
\end{itemize}

Again, please reach out to us if you are interested.


\section{Linux Workshop}
\label{sec:orgheadline9}

This Wednesday, September 14, Ujjwal will be running a linux workshop during
the CS club meeting, i.e., 3 pm to 4 pm in BUH104.

We will cover basic Linux commands and demonstrate a workflow to develop C++
and Python programs.

There will be further Linux workshops covering other workflows and more advanced
topics later on. Especially if there is demand.

\begin{description}
\item[{WHAT:}] Linux Workshop
\item[{WHY:}] Learn a new Operating System that is much more streamlined for programming
\item[{WHEN:}] 3 pm to 4 pm, September 14
\item[{WHERE:}] BUH104
\end{description}


\section{Study Groups}
\label{sec:orgheadline10}

Interested students can form study groups together with upper level
students. For starters, we have some volunteers who are willing to help people
in their dorms. You would work with other people in the group at your
leisure. We will have larger meetings where multiple groups can come together
to hang out or present their progress or anything of curiosity.

Please indicate in the form being passed around if you are interested. Make
note of the dorms you are in and we will hook you up with mentors living in the
same building as you. Off campus students can meet with off campus mentors
also!


\section{Company visit}
\label{sec:orgheadline11}

Our department has a strong relationship with the local companies of note. We
visited one of the biggest local companies, MidwayUSA, last semester. They have
a large number of our graduates working for them.

We will visit a new company this semester also. More details coming soon.


\section{Hackathon}
\label{sec:orgheadline12}

Hackathons are fun events where programmers attempt to hack together a
prototype in a limited time for something they are interested in. We are aiming
to organize an internal Hackathon this semester. More details to follow. If you
are interested, come talk to us.

\begin{description}
\item[{WHAT:}] CC Hackathon
\item[{WHY:}] Share your awesome application idea and hack a prototype in a day
\item[{WHEN:}] To be decided
\item[{WHERE:}] To be decided
\end{description}


\section{CS T-shirt}
\label{sec:orgheadline13}

You must have seen people walking around wearing the CS T-shirt. We are going
to make sure anyone here who wants one gets one. If you do want one, please
indicate that in the form being passed around.

\begin{description}
\item[{WHAT:}] CS T-shirts
\item[{WHY:}] Wear the club with pride and have a souvenir for later years
\item[{WHEN:}] Middle/Late October
\item[{PRICE}] To Be Decided (\textasciitilde{}\$13)
\end{description}


\section{Fund Raising}
\label{sec:orgheadline14}

Ideas and volunteers welcome. Make it fun if possible.


\newpage


\section{Your information}
\label{sec:orgheadline15}

Turn this page in to one of the CS officers if you aren't already in our Google
Group.

\begin{description}
\item[{Name:}] 

\item[{Email:}] 

\item[{Major:}] 

\item[{Year in school:}] 

\item $\square$ Please add me to the cc\_cs Google Group.
\item $\square$ I am interested in buying the CS club T-shirt.
\item $\square$ I am interested in volunteering for one or more cs club events.
\item $\square$ I am interested in forming a study group with other students.
\item[{Dorm:}] 

\item $\square$ Banks
\item $\square$ Miller
\item $\square$ Hughes
\item $\square$ Off-campus
\end{description}


\end{document}
\end{document}
